---
title: 'yield_total'
author: ""
date: "`r format(Sys.time(), '%m-%d-%Y')`"
output: html_document
params:
  filename: filename
  mapType: mapType
  GeoLines: GeoLines
  lineShape: lineShape
  k: k
  vvar: vvar
  existGeoLines: existGeoLines
  Rshiny: Rshiny
  input: input
  predictionTitleSize: predictionTitleSize
  scenario_name: scenario_name
  scenario_map_list: scenario_map_list
  master_map_list: master_map_list
  predictionLegendSize: predictionLegendSize
  mapunits.list: mapunits.list
  predictionLegendBackground: predictionLegendBackground
  break1: break1
  Mcolors: Mcolors
  enable_plotlyMaps: enable_plotlyMaps
  output_map_type: output_map_type
  lineWidth: lineWidth
  lon_limit: lon_limit
  lat_limit: lat_limit
  nlty: nlty
  nlwd: nlwd
  dmapfinal: dmapfinal
  mapdataname: mapdataname
  subdata: subdata
  predictionMapColors: predictionMapColors
  add_plotlyVars: add_plotlyVars
  commonvar: commonvar
  mapScenarios: mapScenarios
  predictionMapBackground: predictionMapBackground
  LineShapeGeo: LineShapeGeo
  mapvarname: mapvarname
  predictionClassRounding: predictionClassRounding
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,eval=TRUE, echo=FALSE,warning=FALSE, message = FALSE)
```

```{r, eval=TRUE, echo=FALSE,warning=FALSE, message = FALSE}
#unpack params
filename<-params$filename
mapType<-params$mapType
GeoLines<-params$GeoLines
lineShape<-params$lineShape
k<-params$k
vvar<-params$vvar
existGeoLines<-params$existGeoLines
Rshiny<-params$Rshiny
input<-params$input
predictionTitleSize<-params$predictionTitleSize
scenario_name<-params$scenario_name
scenario_map_list<-params$scenario_map_list
master_map_list<-params$master_map_list
predictionLegendSize<-params$predictionLegendSize
mapunits.list<-params$mapunits.list
predictionLegendBackground<-params$predictionLegendBackground
break1<-params$break1
Mcolors<-params$Mcolors
enable_plotlyMaps<-params$enable_plotlyMaps
output_map_type<-params$output_map_type
lineWidth<-params$lineWidth
lon_limit<-params$lon_limit
lat_limit<-params$lat_limit
nlty<-params$nlty
nlwd<-params$nlwd
dmapfinal<-params$dmapfinal
mapdataname<-params$mapdataname
subdata<-params$subdata
predictionMapColors<-params$predictionMapColors
add_plotlyVars<-params$add_plotlyVars
commonvar<-params$commonvar
mapScenarios<-params$mapScenarios
predictionMapBackground<-params$predictionMapBackground
LineShapeGeo<-params$LineShapeGeo
mapvarname<-params$mapvarname
predictionClassRounding<-params$predictionClassRounding

if (enable_plotlyMaps=="no"){
  pdf(filename) 
}else{#plotlystuff
  if (mapScenarios==FALSE){
    titleStr<-master_map_list[k]
  }else{
    if (Rshiny==FALSE){
      titleStr<-paste(scenario_name,scenario_map_list[k],sep=" ")
    }else{
      titleStr<-paste(input$scenarioName,master_map_list[k],sep=" ")
    }
  }
  
  #start plotly plot
  p<-plot_ly() %>%
    layout(
      showlegend =TRUE,
      xaxis = list(range = lon_limit,
                   showticklabels= TRUE,
                   title = "Longitude"),
      yaxis = list(range = lat_limit,
                   showticklabels = TRUE,
                   title = "Latitude"),
      title = titleStr)
}

if (existGeoLines==TRUE){
  #load(pathGeoLines)
  if (enable_plotlyMaps=="no"){
    plot(st_geometry(GeoLines),lwd=0.1,xlim=lon_limit,ylim=lat_limit,col = predictionMapBackground)
  }else{
    p <- p %>% add_sf(data = GeoLines,  mode = "lines", type = "scatter",
                      stroke = I("black"),color = I(predictionMapBackground),
                      name = LineShapeGeo)
    
    
    
  }
}



if (mapType=="stream"){
  # select the shading colors for a given mapping variable
  
  
  
  if (enable_plotlyMaps=="no"){
    mapvarname <- paste("lineShape$MAPCOLORS",k,sep="")
    if (existGeoLines==TRUE){
      
      xtext <- paste("plot(st_geometry(lineShape),col=",mapvarname,",lwd=lineWidth, add=TRUE)",sep="")
      eval(parse(text=xtext))
    } else {
      xtext <- paste("plot(st_geometry(lineShape),col=",mapvarname,",lwd=lineWidth,bg = predictionMapBackground))",sep="")
      eval(parse(text=xtext))
    }
  }else{#plotly
    uniqueCols<-eval(parse(text = paste0("as.character(unique(lineShape$",mapvarname,"))")))
    uniqueCols<-predictionMapColors[predictionMapColors %in% uniqueCols]
    for (c in uniqueCols){
      lineShape$mapColor<-eval(parse(text = paste0("lineShape$",mapvarname)))
      mapdata<-lineShape[lineShape$mapColor==c,]
      mapdata$mapdataname<-eval(parse(text = paste0("mapdata$",mapdataname)))     
      
      #data<-merge(mapdata,subdata, by.x = commonvar, by.y = "waterid_for_RSPARROW_mapping")
      #names(data)[names(data)==commonvar]<-"waterid_for_RSPARROW_mapping"
      #data<-data[,names(data) %in% names(subdata)]
      
      lineText<-"~paste('</br> Lat: ',lat,
                   '</br> Lon: ',lon,
                   '</br> ',master_map_list[k],' :',
                   round(mapdataname,predictionClassRounding)"
      
      lineText<-addMarkerText(lineText,add_plotlyVars,mapdata, NA)$markerText
      #mapdata<-addMarkerText(lineText,add_plotlyVars, mapdata, data)$mapData
     
      p <- p %>% add_sf(data = mapdata, mode = "lines", type = "scatter",
                        color = I(c),
                        name = break1[k][[1]][uniqueCols==c],
                        line = list(width = lineWidth),
                        hoverinfo = 'text',
                        text = eval(parse(text = lineText)))
    }

    #p

  }
}else{#catchment
  
}

if (enable_plotlyMaps=="no"){
  if (mapScenarios==FALSE){
    title(master_map_list[k],cex.main = predictionTitleSize)
  }else{
    if (Rshiny==FALSE){
      title(paste(scenario_name,scenario_map_list[k],sep=" "))
    }else{
      title(paste(input$scenarioName,master_map_list[k],sep=" "),cex.main = predictionTitleSize) 
    }
  }
  
  
  
  legend("bottomleft",break1[k][[1]],lty=nlty,cex=predictionLegendSize,title=mapunits.list[k],
         bg=predictionLegendBackground,lwd=nlwd, col=Mcolors[1:length(break1[k][[1]])], bty="o")
  
  
  dev.off()
  if (k==length(master_map_list)){
    if (regexpr("catchment",paste(output_map_type,collapse=","))<0){
      if (input$batch=="Batch" & Rshiny==TRUE) {
        shell.exec(filename) 
      }
      
    }
  }
}


